Discovery of s-process stars in the LAMOST survey

### 2018-01-24 article/ms.tex
abstract edits and minor spelling

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as Barium stars. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These stars are generally thought to have accreted mass from a more evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars is uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates including; 257 Barium stars, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement from 454,180 giant stars observed by LAMOST. This sample constitutes the largest sample of s-process enhanced stars discovered to date, and the most comprehensive search for Barium stars in the Milky Way. \todo{Nearly all} of our Barium stars are disk stars, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory. 51 Barium stars exhibited tecnetium enhancement in a single Tc emission line suggesting the exsistence of AGB stars in our sample. Most (178/257) of our sample show strong carbon enhancement consistent with the literature. Despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in \todo{massive} AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. \todo{This implies ....}
\end{abstract}

@@

Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun. Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occuring in a small phase range as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

>>>>

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 Barium stars, 49 stars exhibiting only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered, and represents the most comprehensive search for Barium stars in the Milky Way. All of our Barium stars are consistent with membership in the Milky Way disk, and we find an \todo{steady/increasing/decreasing} fraction of Barium stars with stellar metallicity, as \todo{expected} from AGB yields and stellar evolution theory. We find 51 Barium stars exhibit some evidence of technetium, \todo{suggesting the existence of AGB stars in our sample}. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of enhancement in sodium. \todo{A sentence about AGB yield comparison.} When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}

@@

Barium stars as first recognised by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun. Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.
